Argennon: A Scalable Smart Contract Platform

### 2021-06-23 tex/A.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Change the structure of chapters
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

    \chapter{Infrastructure}\label{ch:infrastructure}

    \section{Persistence Layer}\label{sec:persistence-layer}
    \input{sections/persistence}

    \section{Networking Layer}\label{sec:networking-layer}
    Unlike conventional blockchains, Argennon does not use a p2p network architecture. Instead, it uses a
    client-server topology, based on a permission-less list of ZK-EDB servers. ZK-EDB servers are a
    crucial part of the Argennon ecosystem, and they form the backbone of the Argennon networking layer.
    \note{not yet written...}

    \subsection{Censorship Resilient Mode}\label{subsec:cens-res-mode}
    \note{not yet written...}

@@

    \section{Concurrency}\label{sec:concurrency}
    \input{sections/concurrency}

    \section{Governance}\label{sec:governance}
    The Argennon Decentralized Autonomous Governance system (ADAGs)
    \note{not yet written...}

\end{document}

>>>>

    \chapter{Persistence Layer}\label{ch:persistance}
    \input{sections/persistence}

    \chapter{Networking Layer}\label{ch:networking}
    Unlike conventional blockchains, Argennon does not use a P2P network architecture. Instead, it uses a
    client-server topology, based on a permission-less list of ZK-EDB servers. ZK-EDB servers are a
    crucial part of the Argennon ecosystem, and they form the backbone of the Argennon networking layer.
    \note{not yet written...}

    \section{Censorship Resilient Mode}\label{sec:cens-res-mode}
    \note{not yet written...}

@@

    \section{Concurrent Transaction Validation}\label{sec:concurrency}
    \input{sections/concurrency}

    \chapter{Governance}\label{ch:governance}
    The Argennon Decentralized Autonomous Governance system (ADAGs)
    \note{not yet written...}
\end{document}

### 2021-06-23 tex/sections/persistence.tex
Change the structure of chapters
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

\subsection{Storage Pages}\label{subsec:pages}

@@

\subsection{Zero-knowledge Databases}\label{subsec:zk-edb}

@@

\subsubsection[Implementation]{Implementation Based on Vector Commitments}\label{subsubsec:impl-zk-edbs}

@@

\subsection{Object Clustering Algorithm}\label{subsec:clustering}

>>>>

@@

\section{Zero-knowledge Databases}\label{sec:zk-edb}

@@

\subsection[Implementation]{Implementation Based on Vector Commitments}\label{subsec:impl-zk-edbs}

@@

\section{Object Clustering Algorithm}\label{sec:clustering}
